---
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
```


Tools for converting R expressions to latex mathematical equations. This project
is scratch from the [section 21.3 transforms mathematically R code into its LaTeX
equivalent](https://adv-r.hadley.nz/translation.html#latex).

## Usage

### Special symbols

```{r special-symbols}
library(rlatexmath)
translate_latexmath(pi)

# quoted object
translate_latexmath_(quote(pi))
```


### Know funcitons

 R expression     |latex math                                
-------------------|------------------------------------------
<b>Binary operators</b>|
x + y                |`r translate_latexmath(x+y)`
x - y                |`r translate_latexmath(x - y)`
x \* y                |`r translate_latexmath(x * y)`
x / y                |`r translate_latexmath(x / y)`
x %+-% y             |`r translate_latexmath(x %+-% y)`
x %/% y             |`r translate_latexmath(x %/% y )`
x %\*% y             |`r translate_latexmath(x %*% y )`
x %.% y             |`r translate_latexmath(x %.% y )`
x[i]                |`r translate_latexmath(x[i])`
x^i                |`r translate_latexmath(x^i)`
<b>Grouping</b>|
(x + y)             |`r translate_latexmath((x+y))`
{x y}               |`r translate_latexmath({x + y})`
<b>Juxtaposition</b>|
paste(x, y, z)      |`r translate_latexmath(paste(x, y, z))`
<b>Comma separated lists</b>|
list(x + y, z)      |`r translate_latexmath(list(x + y, z))`
<b>Fractions</b>|
frac(x, y)          |`r translate_latexmath(frac(x, y))`
atop(x, y)          |`r translate_latexmath(atop(x, y))`
<b>Ellipsis</b>|
list(x[1], cdots, x[2])|`r translate_latexmath(list(x[1], cdots, x[2]))`
list(x[1], ldots, x[2])|`r translate_latexmath(list(x[1], ldots, x[2]))`
<b>Radicals</b>|
sqrt(x)             |`r translate_latexmath(sqrt(x))`
sqrt(x, y)          |`r translate_latexmath(sqrt(x, y))`
<b>Relation</b>|
x == y              | `r translate_latexmath(x == y)`
x != y              | `r translate_latexmath(x != y)`
x < y              | `r translate_latexmath(x < y)`
x > y              | `r translate_latexmath(x > y)`
x >= y              | `r translate_latexmath(x >= y)`
x <= y              | `r translate_latexmath(x <= y)`
x %==% y              | `r translate_latexmath(x %==% y)`
x %~~% y              | `r translate_latexmath(x %~~% y)`
x %=~% y              | `r translate_latexmath(x %=~% y)`
x %prop% y              | `r translate_latexmath(x %prop% y)`
<b>Set</>|
x %supset% y            | `r translate_latexmath(x %supset% y)`
x %supseteq% y            | `r translate_latexmath(x %supseteq% y)`
x %subset% y            | `r translate_latexmath(x %subset% y)`
x %notsubset% y            | `r translate_latexmath(x %notsubset% y)`
x %subseteq% y            | `r translate_latexmath(x %subseteq% y)`
x %in% y            | `r translate_latexmath(x %in% y)`
x %notin% y            | `r translate_latexmath(x %notin% y)`
<b>Arrow</b> |
x %<->% y          |`r translate_latexmath(x %<->% y)`
x %<-% y           |`r translate_latexmath(x %<-% y)`
x %up% y           |`r translate_latexmath(x %up% y)`
x %->% y           |`r translate_latexmath(x %->% y)`
x %down% y         |`r translate_latexmath(x %down% y)`
x %<=>% y          |`r translate_latexmath(x %<=>% y)`
x %<=% y           |`r translate_latexmath(x %<=% y)`
x %dblup% y        |`r translate_latexmath(x %dblup% y)`
x %=>% y           |`r translate_latexmath(x %=>% y)`
x %dbldown% y      |`r translate_latexmath(x %dbldown% y)`
<b>Accent</b>|
tilde(x)|`r translate_latexmath(tilde(x))`
hat(x)|`r translate_latexmath(hat(x))`
widetilde(x)|`r translate_latexmath(widetilde(x))`
widehat(x)|`r translate_latexmath(widehat(x))`
bar(x)|`r translate_latexmath(bar(x))`
<b>Operators</b>|
sum(x[i])| `r translate_latexmath(sum(x[i]))`sum(x[i], i==1, n)| `r translate_latexmath(sum(x[i], i==1, n))`
prod(x[i])| `r translate_latexmath(prod(x[i]))`
prod(x[i], i==1, n)| `r translate_latexmath(prod(x[i], i==1, n))`
integral(f(x)\*{dx}, a, b)| `r translate_latexmath(integral(x*{dx}, a, b))`
union(A[i], i==1, n)| `r translate_latexmath(union(A[i], i==1, n))`
intersect(A[i], i==1, n)| `r translate_latexmath(union(A[i], i==1, n))`
lim(f(x), x %->% infty)| `r translate_latexmath(lim(x, x %->% infty))`
min(f(x), x >= 0)|`r translate_latexmath(min(x, x >= 0))`
max(f(x), x >= 0)|`r translate_latexmath(max(x, x >= 0))`
<b>Typeface</b>|
plain(x)| `r translate_latexmath(plain(x))`
bold(x)| `r translate_latexmath(bold(x))`
italic(x)| `r translate_latexmath(italic(x))`
bolditalic(x)| `r translate_latexmath(bolditalic(x))`
<b>Delimiters</b>|
group("(", list(a,b), "]")|`r translate_latexmath(group("(", list(a,b), "]"))`
bgroup("[", frac(a,b), "]")|`r translate_latexmath(bgroup("[", frac(a,b), "]"))`
abs(x)| `r translate_latexmath(abs(x))`

## related projects

- [equatiomatic](https://github.com/datalorax/equatiomatic)
- [latex2exp](https://github.com/stefano-meschiari/latex2exp)
- [textables](https://github.com/setzler/textables)

## Acknowledgements

- [Hadley Wickham's book advanced R](https://adv-r.hadley.nz/translation.html#latex). 
Both the idea and the code are scratch from this book.

